---
title: "Signed in User"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Signed in User}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
user <- list(signed_in = TRUE, user = list(uid = "XXxxX", 
    displayName = "John", photoURL = "https://lh3.googleusercontent.com/a-/XXxxX", 
    email = "myemail@gmail.com", emailVerified = TRUE, phoneNumber = NULL, 
    isAnonymous = FALSE, tenantId = NULL, providerData = list(
        list(uid = "XXxxX", displayName = "John Coene", 
            photoURL = "https://lh3.googleusercontent.com/a-/XXxxX", 
            email = "jcoenep@gmail.com", phoneNumber = NULL, 
            providerId = "google.com")), apiKey = "XXxxX", 
    appName = "[DEFAULT]", authDomain = "my-package.firebaseapp.com", 
    stsTokenManager = list(apiKey = "XXxxX", 
        refreshToken = "XXxxX", 
        accessToken = "XXxxX", 
        expirationTime = 1584898232000), redirectEventId = NULL, 
    lastLoginAt = "1584894612585", createdAt = "1584894612585", 
    multiFactor = list(enrolledFactors = list())))
```

## Sign in

You can always access the signed in user with the `get_signed_in` method. This returns a list of length 2:

1. `signed_in`: boolean
2. `user`: a list (`NULL` if signed out)

The user object returned looks like.

```{r, echo = FALSE}
print(user)
```

Note this is technically like a Shiny input and behaves as such. Therefore the snippet below will work. Note that it will be triggered on load.

```r
# initialise
f <- FireblazeUI$new()$launch()

observeEvent(f$get_signed_in(), {
  # do somethind
})
```

However one should probably only rely on the `get_signed_in` to retrieve information about the logged in user, the methods `is_signed_in` and `req_sign_in` should be used in observers instead. The first returns `TRUE` if the user is signed in. The second, `req_sign_in` is a convenience method which essentially does `req(f$is_signed_in)` which allows "marking" outputs and observers that require sign in. 

## Sign out

A single method is shared across all authentication methods, simply call `sign_out` method.
